### 2015-11-18 Irregular-occ/Irregular-occ.tex
.

\title{Stellar occultation predictions for  9 irregular satellites of giant planets and Triton for 2015-2017
%\fnmsep\thanks{Table 8 are only available in electronic form at the CDS via anonymous ftp to cdsarc.u-strasbg.fr (130.79.128.5) or via http://cdsweb.u-strasbg.fr/cgi-bin/qcat?J/A+A/ and IAU NSDC data base at www.imcce.fr/nsdc.}
%\fnmsep\thanks{The complete version of Table 8 is available through CDS and IAU NSDC data base at www.imcce.fr/nsdc.}
%\fnmsep\thanks{Partially based on observations made at Laborat\'orio Nacional de Astrof\'{\i}sica (LNA), Itajub\'a-MG, Brazil.}
%\fnmsep\thanks{Partially based on observations through the ESO runs 079.A-9202(A), 075.C-0154, 077.C-0283 and 079.C-0345.}
%\fnmsep\thanks{\textbf{Partially based on observations made at Observatoire de Haute Provence (OHP), F-04870 Saint-Michel l'observatoire, France}}
}

@@

\abstract
{Due to their orbital configurations, it is common belief that the irregular satellites were probably captured by the giant planets in the early solar system. It is important to know their physical parameters, such as size, albedo and composition, to trace back their true origin. The best ground-based technique to constrain those parameters is the observation of stellar occultations by these objects.}
{We aim to predict stellar occultations for the seven biggest irregular satellites of Jupiter: Himalia, Elara, Pasiphae, Carme, Lysithea, Sinope, Ananke and Leda; the irregular satellite of Saturn: Phoebe; and the satellites of Neptune: Nereid and Triton.}
{We identified candidates to stellar occultations by the irregular satellites from the UCAC4 catalogue and from a catalogue of stars in the sky-path of Neptune obtained from observations made with the ESO2p2/WFI (2.2 m Max-Planck ESO telescope with the Wide Field Imager) instrument. These catalogues were crossed with the ephemeris of the satellites to identify stellar occultations. We used a new ephemeris based solely on the observations from \cite{GomesJunior2015} to generate quick predictions for the short-time future for the satellites of Jupiter. For Phoebe, Nereid and Triton we used the JPL ephemeris.}
{We managed to obtain \textcolor{red}{588} candidates of stellar occultations between the period of January, 2015 and December, 2017. We made observational tests for the predictions of the events of Himalia in March 03, 2015 and Elara in March 30, 2015. The stars and objects were observed close to the date predicted and and in the same field to minimize errors and the obtained relative satellite-star positions were used to evaluate the predictions.}
{The comparisons between the predictions and the observation tests show a good agreement. We discuss how the successful observation of a stellar occultation by these objects is quite possible and present some of those potential occultations.}

@@

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{centering}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & mas\tablefootmark{a}  & km & References \tabularnewline
\hline
Ananke & 8 & 29 & 1 \tabularnewline
Carme & 13 & 46 & 1 \tabularnewline
Elara & 24 & 86 & 1 \tabularnewline
Himalia & 41 & $(150\times120) \pm 20$\tablefootmark{b} & 2 \tabularnewline
Leda &  &  & 1 \tabularnewline
Lysithea & 10 & 36 & 1 \tabularnewline
Pasiphae & 17 & 62 & 1 \tabularnewline
Sinope & 10 & 37 & 1 \tabularnewline
\hdashline
Phoebe & 32 & $212 \pm 1.4$\tablefootmark{b} & 3 \tabularnewline
\hdashline
Nereid & 15 & $340 \pm 50$\tablefootmark{c} & 4 \tabularnewline
Triton & 124 & $2707 \pm 2.0$\tablefootmark{c} & 5 \tabularnewline
\hline
\end{tabular}
\tablebib{
(1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}; (4) \cite{Thomas1991}; (5) \cite{Thomas2000}.}
\end{centering}
\tablefoottext{a}{Using a mean distance from Jupiter of 5 AU, from Saturn of 9 AU and from Neptune of 30 AU.}
\tablefoottext{b}{From Cassini observation.}
\tablefoottext{c}{From Voyager-2 observation.}
\par
\end{table}

@@

The initial osculating elements at the origin of integration are presented in Table \ref{Tab: sat_ell}, while the residuals are presented in Fig \ref{omcHim} to \ref{}. %don't remember wich one

@@

\begin{table*}
\caption{Initial osculating elements for Jupiter irregular satellites at JD 2451545.0. For Themisto's case, the small number of observations meant that the statistical uncertainty was even greater than the obtained elements, though the fitting proved satisfying. We decided to provide its elements with significant number comparable to the other satellite for information, but left it without uncertainty.  }\label{Tab: sat_ell}
\begin{center}
\begin{tabular}{ccccccc}
\hline\hline
Satellite & a (km) & e & incl. (EQJ2000) & $\Omega$ & $\omega$ & $v$ \\ 
\hline
Himalia &   11372100 $\pm$ 500    &    0.166 $\pm$ 0.002      &   45.14 $\pm$ 0.15      &   39.77 $\pm$ 0.19      &   351.48 $\pm$ 0.46      &   97.35 $\pm$ 0.48    \\
Elara &   11741170 $\pm$ 690  &      0.222 $\pm$ 0.002      &   28.64 $\pm$ 0.18      &   68.42 $\pm$ 0.43      &   179.82 $\pm$ 0.56      &   339.08 $\pm$ 0.82  \\
Lysithea &   11739900 $\pm$ 1300  &      0.136 $\pm$ 0.004      &    51.12 $\pm$ 0.27     &   5.53 $\pm$ 0.52      &   53.0 $\pm$ 1.5      &   318.9 $\pm$ 2.0   \\
Leda &   11140300  $\pm$ 4300  &     0.173  $\pm$ 0.007     &   16.15  $\pm$ 0.75    &   272.6  $\pm$ 1.7    &   212.2  $\pm$ 3.6          &   218.8  $\pm$ 3.2  \\
Pasiphae &  23425000  $\pm$ 5000    &     0.379  $\pm$ 0.001       &   152.44 $\pm$ 0.10      &   284.59 $\pm$ 0.21      &   135.96 $\pm$ 0.19      &   236.97 $\pm$ 0.16 \\
Sinope &   22968800 $\pm$ 5200   &     0.316 $\pm$ 0.002      &   157.76 $\pm$ 0.12      &   256.62 $\pm$ 0.55      &   298.38 $\pm$ 0.55      &   167.57 $\pm$ 0.19    \\
Carme &   24202924 $\pm$ 4800      &  0.242 $\pm$ 0.001      &   147.13 $\pm$ 0.10      &   154.01 $\pm$ 0.25      &   47.90 $\pm$ 0.29      &   234.41 $\pm$ 0.19  \\
Ananke &  21683800  $\pm$ 7200  &     0.380 $\pm$ 0.002      &   172.29 $\pm$ 0.20      &   56.9 $\pm$ 1.2      &   123.3 $\pm$ 1.2      &   231.24 $\pm$ 0.21  \\
%Themisto  & 7393800    &     0.198       &   25.77  &   220.0     &   216.3    &   262.1     \\
\hline
\end{tabular}

@@

\textcolor{red}{Here we write something about the numerical integration}

@@

A total of 588 events \textcolor{red}{(Not counting Triton's event yet)} were identified between January 2015 and December 2017. In table \ref{Tab: satellite-occultation} we present the number of stellar occultations predicted by year for each satellite. Table \ref{Tab: occ-list} shows a sample of the catalogue of occultations generated and their parameters, which are necessary to produce occultation maps (see Fig. \ref{Fig: ocultacao} as an example). Since these objects are very small, the duration of each event is a few seconds.

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from 2015 up to 2017.}
\begin{centering}
\begin{tabular}{lcccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2015  & 2016 & 2017 & Total \tabularnewline
\hline
Ananke & 22 & 12 & 16 & 50 \tabularnewline
Carme & 25 & 20 & 14 & 59 \tabularnewline
Elara & 32 & 14 & 16 & 62 \tabularnewline
Himalia & 25 & 15 & 12 & 52 \tabularnewline
Lysithea & 22 & 16 & 11 & 49 \tabularnewline
Pasiphae & 26 & 19 & 20 & 65 \tabularnewline
Sinope & 19 & 15 & 21 & 55 \tabularnewline
Leda &  &  &  &  \tabularnewline
\hdashline
Phoebe\tablefootmark{a} & 13 & 32 & 98 & 143 \tabularnewline
\hdashline
Nereid\tablefootmark{a} & 41\tablefootmark{b} & 11\tablefootmark{b} & 1 & 53 \tabularnewline
Triton\tablefootmark{a} & \tablefootmark{b} & \tablefootmark{b} &  &  \tabularnewline
\hline
\end{tabular}
\par \end{centering}
Occultations predicted using the UCAC4 catalogue and STE ephemeris.
\tablefoottext{a}{Using JPL ephemeris.}
\tablefoottext{b} {Using the WFI catalogue as explained in Sec. \ref{Sec: predictions}} \textcolor{red}{Numbers of Triton yet to be written}.
\end{table}

\begin{table*}
\caption{\label{Tab: sample-cds} Stellar occultation sampled predictions for Himalia \textcolor{red}{I still have to fix the table}}
\begin{centering}
\begin{tabular}{ccccccccccccccccccccccc}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline
d m Year & h m s & \multicolumn{2}{c}{RA (ICRS) Dec} & C/A & P/A & v & D & R* & $\lambda$ & LST & $\Delta e_{\alpha *}$ & $\Delta e_{\delta}$ & pm & ct & $E_{\alpha *}$ & $E_{\delta}$ & $\mu_{\alpha *}$ & $\mu_{\delta}$ \tabularnewline
\hline
 07 10 2015 & 21 52 34. &  10 53 40.1835 & +08 21  00.489 & 0.465 & 200.31 & 39.31 & 6.25 & 16.6 & 179. & 09:48 & -31.0 & -13.0 & ok & uc &   0  &  0 & -13 &  -7 \tabularnewline
 23 10 2015 & 07 54 50. &  11 05 26.6037 & +07 14  32.030 & 1.017 & 201.33  & 36.11 & 6.12 & 15.5 & 16. & 08:59 & -31.0 & -13.0 & ok & uc &  0  &  0 &  -7 &  -4 \tabularnewline
 31 10 2015 & 00 24 19. &  11 10 56.2964 & +06 42  07.110 &  1.801 &  21.84 & 33.94 &  6.04 & 16.9 &  123. & 08:34 & -31.0 & -13.0 & ok & uc & 0  &  0 & -4 & -13 \tabularnewline
 07 11 2015 &  21 22 53. &  11 16 14.3041 & +06 10  05.194 &  0.306 &  202.36 & 31.33 & 5.94 & 16.2 & 162. & 08:09 & -31.0 & -13.0 & ok & uc & 0 & 0 & 0 & 0 \tabularnewline
 08 11 2015 & 04 27 21. &  11 16 25.7881 & +06 08  55.566 & 1.077 & 202.38 & 31.23 & 5.94 & 16.9 & 55. & 08:08 & -31.0 & -13.0 & ok & uc & 0 & 0 & 9 & -10 \tabularnewline
% 09 11 2015  09 01  4.   11 17 11.6890 +06 04  11.474   11 17 11.7030 +06 04  11.980   0.549   22.45  30.79  5.92 15.9  0.5  0.5  0.5   346. 08:04     -31.0    -13.0 ok uc 0    0    0   19  -13 \tabularnewline
% 11 11 2015  12 58 46.   11 18 33.8286 +05 55  43.695   11 18 33.8357 +05 55  43.946   0.274   22.59  29.98  5.90 14.6  0.4  0.4  0.4   285. 07:57     -31.0    -13.0 ok uc 0    0    0  -14    1 \tabularnewline
% 12 11 2015  20 14 22.   11 19 22.2740 +05 50  40.732   11 19 22.3183 +05 50  42.312   1.713   22.68  29.48  5.88 15.7  0.4  0.4  0.4   175. 07:52     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 04 12 2015  03 31 56.   11 30 41.9967 +04 37  36.039   11 30 42.0020 +04 37  36.217   0.196   24.18  20.14  5.56 15.0  0.0  0.0  0.0    47. 06:40     -31.0    -13.0 ok uc 0    0    0    5   -9 \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\textbf{Notes}. Entries included: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table, these coordinates are immediately followed by the geocentric astrometric equatorial coordinates of the satellite (corrected the computed ephemeris offset derived in Sec. \ref{Sec: integration}); C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; D: planet range to Earth, in AU; R*: normalized magnitude to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{Mag}* = \textrm{Mag}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$. A value of 50.0 means that the star is not in the 2MASS; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\Delta e_{\alpha *}$ and $\Delta e_{\delta}$: computed offsets in mas applied to the ephemeris right ascension and declination, respectively; pm: ok = proper motion applied, no = no proper motion applied; catalogue cross-identification (ct) = uc (UCAC2), 2m (2MASS), fs (field star); $E_{\alpha *}$ and $E_{\delta}$: uncertainties (mas) in right ascension and declination. A value of 9999 means that there was no estimation of the respective uncertainty; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

\begin{figure*}
\begin{centering}
\includegraphics[scale=0.4]{figures/Pasiphae_2016-04-09T03:58:19.png}   
\caption{Occultation map for Himalia regarding to the second event sampled in Table \ref{Tab: occ-list}}
\label{Fig: ocultacao}
\end{centering}
\end{figure*}

>>>>

\title{Stellar occultation predictions for  10 irregular satellites of giant planets and Triton for 2015-2017
%\fnmsep\thanks{Table 8 are only available in electronic form at the CDS via anonymous ftp to cdsarc.u-strasbg.fr (130.79.128.5) or via http://cdsweb.u-strasbg.fr/cgi-bin/qcat?J/A+A/ and IAU NSDC data base at www.imcce.fr/nsdc.}
%\fnmsep\thanks{The complete version of Table 8 is available through CDS and IAU NSDC data base at www.imcce.fr/nsdc.}
%\fnmsep\thanks{Partially based on observations made at Laborat\'orio Nacional de Astrof\'{\i}sica (LNA), Itajub\'a-MG, Brazil.}
%\fnmsep\thanks{Partially based on observations through the ESO runs 079.A-9202(A), 075.C-0154, 077.C-0283 and 079.C-0345.}
%\fnmsep\thanks{\textbf{Partially based on observations made at Observatoire de Haute Provence (OHP), F-04870 Saint-Michel l'observatoire, France}}
}

@@

\abstract
{Due to their orbital configurations, it is common belief that the irregular satellites were probably captured by the giant planets in the early solar system. It is important to know their physical parameters, such as size, albedo and composition, to trace back their true origin. The best ground-based technique to constrain those parameters is the observation of stellar occultations by these objects.}
{We aim to predict stellar occultations for the seven biggest irregular satellites of Jupiter: Himalia, Elara, Pasiphae, Carme, Lysithea, Sinope, Ananke and Leda; the irregular satellite of Saturn: Phoebe; and the satellites of Neptune: Nereid and Triton.}
{We identified candidates to stellar occultations by the irregular satellites from the UCAC4 catalogue and from a catalogue of stars in the sky-path of Neptune obtained from observations made with the ESO2p2/WFI (2.2 m Max-Planck ESO telescope with the Wide Field Imager) instrument. These catalogues were crossed with the ephemeris of the satellites to identify stellar occultations. We used a new ephemeris based solely on the observations from \cite{GomesJunior2015} to generate quick predictions for the short-time future for the satellites of Jupiter. For Phoebe, Nereid and Triton we used the JPL ephemeris.}
{We managed to identify 687 candidates of stellar occultations between the period of January, 2015 and December, 2017. We made observational tests for the predictions of the events of Himalia in March 03, 2015 and Elara in March 30, 2015. The stars and objects were observed close to the date predicted and in the same field to minimize errors and the obtained relative satellite-star positions were used to evaluate the predictions.}
{The comparisons between the predictions and the observation tests show a good agreement. We discuss how the successful observation of a stellar occultation by these objects is quite possible and present some of those potential occultations.}

@@

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{centering}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & mas\tablefootmark{a}  & km & References \tabularnewline
\hline
Ananke & 8 & 29 & 1 \tabularnewline
Carme & 13 & 46 & 1 \tabularnewline
Elara & 24 & 86 & 1 \tabularnewline
Himalia & 41 & $(150\times120) \pm 20$\tablefootmark{b} & 2 \tabularnewline
Leda & 5 & 20 & 1 \tabularnewline
Lysithea & 10 & 36 & 1 \tabularnewline
Pasiphae & 17 & 62 & 1 \tabularnewline
Sinope & 10 & 37 & 1 \tabularnewline
\hdashline
Phoebe & 32 & $212 \pm 1.4$\tablefootmark{b} & 3 \tabularnewline
\hdashline
Nereid & 15 & $340 \pm 50$\tablefootmark{c} & 4 \tabularnewline
Triton & 124 & $2707 \pm 2.0$\tablefootmark{c} & 5 \tabularnewline
\hline
\end{tabular}
\tablebib{
(1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}; (4) \cite{Thomas1991}; (5) \cite{Thomas2000}.}
\end{centering}
\tablefoottext{a}{Using a mean distance from Jupiter of 5 AU, from Saturn of 9 AU and from Neptune of 30 AU.}
\tablefoottext{b}{From Cassini observation.}
\tablefoottext{c}{From Voyager-2 observation.}
\par
\end{table}

@@

The initial osculating elements at the origin of integration are presented in Table \ref{Tab: sat_ell}, while the residuals are presented in Fig \ref{Fig: residuals} for Himalia and Carme.

\begin{figure*}
\subfigure{\includegraphics[width=8.8cm]{Laurene/residuals/Himalia_resid.eps}   \label{Fig: residuals-Himalia}}
\subfigure{\includegraphics[width=8.8cm]{Laurene/residuals/Carme_resid.eps}  \label{Fig: residuals-Carme}}
\caption{Residuals of Himalia and Carme \label{Fig: residuals}}
\end{figure*}

@@

\begin{table*}
\caption{Initial osculating elements for Jupiter irregular satellites at JD 2451545.0.% For Themisto's case, the small number of observations meant that the statistical uncertainty was even greater than the obtained elements, though the fitting proved satisfying. We decided to provide its elements with significant number comparable to the other satellite for information, but left it without uncertainty.
 }\label{Tab: sat_ell}
\begin{center}
\begin{tabular}{ccccccc}
\hline\hline
Satellite & a (km) & e & incl. (EQJ2000) & $\Omega$ & $\omega$ & $v$ \\ 
\hline
Himalia &   11372100 $\pm$ 500    &    0.166 $\pm$ 0.002      &   45.14 $\pm$ 0.15      &   39.77 $\pm$ 0.19      &   351.48 $\pm$ 0.46      &   97.35 $\pm$ 0.48    \\
Elara &   11741170 $\pm$ 690  &      0.222 $\pm$ 0.002      &   28.64 $\pm$ 0.18      &   68.42 $\pm$ 0.43      &   179.82 $\pm$ 0.56      &   339.08 $\pm$ 0.82  \\
Lysithea &   11739900 $\pm$ 1300  &      0.136 $\pm$ 0.004      &    51.12 $\pm$ 0.27     &   5.53 $\pm$ 0.52      &   53.0 $\pm$ 1.5      &   318.9 $\pm$ 2.0   \\
Leda &   11140300  $\pm$ 4300  &     0.173  $\pm$ 0.007     &   16.15  $\pm$ 0.75    &   272.6  $\pm$ 1.7    &   212.2  $\pm$ 3.6          &   218.8  $\pm$ 3.2  \\
Pasiphae &  23425000  $\pm$ 5000    &     0.379  $\pm$ 0.001       &   152.44 $\pm$ 0.10      &   284.59 $\pm$ 0.21      &   135.96 $\pm$ 0.19      &   236.97 $\pm$ 0.16 \\
Sinope &   22968800 $\pm$ 5200   &     0.316 $\pm$ 0.002      &   157.76 $\pm$ 0.12      &   256.62 $\pm$ 0.55      &   298.38 $\pm$ 0.55      &   167.57 $\pm$ 0.19    \\
Carme &   24202924 $\pm$ 4800      &  0.242 $\pm$ 0.001      &   147.13 $\pm$ 0.10      &   154.01 $\pm$ 0.25      &   47.90 $\pm$ 0.29      &   234.41 $\pm$ 0.19  \\
Ananke &  21683800  $\pm$ 7200  &     0.380 $\pm$ 0.002      &   172.29 $\pm$ 0.20      &   56.9 $\pm$ 1.2      &   123.3 $\pm$ 1.2      &   231.24 $\pm$ 0.21  \\
%Themisto  & 7393800    &     0.198       &   25.77  &   220.0     &   216.3    &   262.1     \\
\hline
\end{tabular}

@@

@@

A total of 687 events were identified between January 2015 and December 2017. In table \ref{Tab: satellite-occultation} we present the number of stellar occultations predicted by year for each satellite. Table \ref{Tab: occ-list} shows a sample of the catalogue of occultations generated and their parameters, which are necessary to produce occultation maps (see Fig. \ref{Fig: ocultacao} as an example). Since these objects are very small, the duration of each event is a few seconds.

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from 2015 up to 2017.}
\begin{centering}
\begin{tabular}{lcccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2015  & 2016 & 2017 & Total \tabularnewline
\hline
Ananke & 21 & 12 & 16 & 49 \tabularnewline
Carme & 26 & 20 & 14 & 60 \tabularnewline
Elara & 32 & 14 & 16 & 62 \tabularnewline
Himalia & 26 & 15 & 12 & 53 \tabularnewline
Leda & 13 & 8 & 24 & 45 \tabularnewline
Lysithea & 22 & 16 & 11 & 49 \tabularnewline
Pasiphae & 25 & 20 & 19 & 64 \tabularnewline
Sinope & 19 & 15 & 21 & 55 \tabularnewline
\hdashline
Phoebe\tablefootmark{a} & 13 & 32 & 98 & 143 \tabularnewline
\hdashline
Nereid\tablefootmark{a} & 41\tablefootmark{b} & 11\tablefootmark{b} & 1 & 53 \tabularnewline
Triton\tablefootmark{a} & 37\tablefootmark{b} & 16\tablefootmark{b} & 1 & 54 \tabularnewline
\hline
\end{tabular}
\par \end{centering}
Occultations predicted using the UCAC4 catalogue and STE ephemeris.
\tablefoottext{a}{Using JPL ephemeris.}
\tablefoottext{b} {Using the WFI catalogue as explained in Sec. \ref{Sec: predictions}}.
\end{table}

\begin{table*}
\caption{\label{Tab: sample-cds} Stellar occultation sampled predictions for Himalia \textcolor{red}{I still have to fix the table}}
\begin{centering}
\begin{tabular}{l}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline

\hline
\end{tabular}
\par\end{centering}
\textbf{Notes}. Entries included: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table, these coordinates are immediately followed by the geocentric astrometric equatorial coordinates of the satellite (corrected the computed ephemeris offset derived in Sec. \ref{Sec: integration}); C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; D: planet range to Earth, in AU; R*: normalized magnitude to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{Mag}* = \textrm{Mag}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$. A value of 50.0 means that the star is not in the 2MASS; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\Delta e_{\alpha *}$ and $\Delta e_{\delta}$: computed offsets in mas applied to the ephemeris right ascension and declination, respectively; pm: ok = proper motion applied, no = no proper motion applied; catalogue cross-identification (ct) = uc (UCAC2), 2m (2MASS), fs (field star); $E_{\alpha *}$ and $E_{\delta}$: uncertainties (mas) in right ascension and declination. A value of 9999 means that there was no estimation of the respective uncertainty; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

\begin{figure*}
\begin{centering}
\includegraphics[scale=0.4]{figures/Pasiphae_2016-04-09T03:58:19.png}   
\caption{Occultation map for Himalia regarding to the fifth event sampled in Table \ref{Tab: occ-list}}
\label{Fig: ocultacao}
\end{centering}
\end{figure*}
